Flowchart of Current Algorithm

### 2008-10-12 docs/flowchart/paper.tex
more tex clean-ups

\begin{enumerate}
\renewcommand{\theenumii}{{\bf \alph{enumii}}}

\item plane-parallel

\begin{enumerate}
\item For the density update, we discretize equation the base state
  density evolution equation
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
- \nablab \cdotb \left( \etarho \er \right) \enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
(paper III; eq.~[29]), neglecting the $\etarho$ term, to compute the
new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ] \nonumber  \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A, and are saved for use
later in the overall algorithm.

@@

\item spherical

@@

@@

\item {\bf Correct Base}$(\rho_0^{\inp} , \etarho^{\inp}) \rightarrow (\rho_0^{\outp})$
is the process by which we adjust the base state density given $\etarho$ using
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left( \eta_{\rho,j+\myhalf}^{\inp} - \eta_{\rho,j-\myhalf}^{\inp}  \right)  \enskip . 
\end{eqnarray} 
\end{enumerate}
\MarginPar{need to add spherical}

@@

\item Construct $w_0^{\nph,\star}$ by integrating

\begin{enumerate}
\renewcommand{\labelenumii}{\roman{enumii}.}
\item plane-parallel
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g \enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh},$ \MarginPar{note: this is true only for plane-parallel}
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}} \psi^{\nmh} \enskip . \nonumber
\end{equation}

\item spherical

\MarginPar{need to add spherical}
\end{enumerate}

@@

@@

\item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2),\star}$ and
$(\rho h)^{(1)} \rightarrow (\rho h)^{(2),\star}$ without explicitly including the 
reaction terms,
\begin{eqnarray}
(\rho X_k)^{(2),\star} &=& (\rho X_k)^{(1)} 
 - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho X_k)^{(1),\nph,\star} \right) \right] \enskip , \\ \nonumber  \\
(\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho h)^{(1),\nph,\star} \right) \right] \nonumber \\
&& + \dt \; \left(\uadvone \cdotb \er\right) \left(\frac{\partial p_0}{\partial r} \right)^{n} 
+ \dt \; \psi^{\nmh} \enskip , \\
\rho^{(2'),\star} &=& \sum_k (\rho X_k)^{(2),\star} \enskip , \\ 
X_k^{(2),\star} &=& (\rho X_k)^{(2),\star} / \rho^{(2),\star}
\end{eqnarray}

\item {\bf Correct Base}$(\rho_0^{(2),\star}, \etarho^{\nmh}) \rightarrow (\rho_0^{n+1,\star})$.

@@

\begin{enumerate}
\renewcommand{\labelenumii}{\roman{enumii}.}

\item plane-parallel

@@

\item spherical

\MarginPar{need to add spherical here}
\end{enumerate}

@@

\item {\bf React State}$( \rho^{(2),\star},(\rho h)^{(2),\star}, X_k^{(2),\star}, 
                             T^{(2),\star}, (\rho^{(2),\star} \Hext)) $\\
$\rightarrow ( \rho^{n+1,\star},(\rho h)^{n+1,\star}, X_k^{n+1,\star}, T^{n+1,\star}, 
              (\rho \omegadot_k)^{(2),\star}, (\rho \Hnuc)^{(2),\star} ).$

@@

\item Construct $w_0^{\nph}$ by integrating equation (\ref{eq:divw0}),

\begin{enumerate}
\renewcommand{\labelenumii}{\roman{enumii}.}

\item plane-parallel

@@

\item spherical

@@

\begin{enumerate}
\renewcommand{\labelenumii}{\roman{enumii}.}

\item plane-parallel

@@

\item {\bf React State}$(\rho^{(2)},(\rho h)^{(2)}, X_k^{(2)},T^{(2)}, (\rho^{(2)} \Hext) )
                   \rightarrow (\rho^{n+1}, (\rho h)^{n+1}, X_k^{n+1}, T^{n+1}, 
                               (\rho \omegadot_k)^{(2)}, (\rho \Hnuc)^{(2)} ).$

@@

  \item {\bf React State}$( \rho^{\initp},(\rho h)^{\initp}, X_k^{\initp}, T^{\initp}, (\rho^{\initp} \Hext) )$\\
      $\rightarrow (\rho^{\outp}, (\rho h)^{\outp}, X_k^{\outp}, T^{\outp}, (\rho \omegadot_k)^{0,\nu} ).$

>>>>

\item[plane-parallel:] ~

\begin{enumerate}
\renewcommand{\labelenumii}{{\bf \alph{enumii}}.}

\item For the density update, we discretize equation the base state
  density evolution equation
\begin{eqnarray}
\frac{\partial \rhozero}{\partial t} &=& - \nablab \cdotb \left( \rhozero w_0 \er \right)
- \nablab \cdotb \left( \etarho \er \right) \enskip ,
\label{eq:rho0upd_new}
\end{eqnarray}
(paper III; eq.~[29]), neglecting the $\etarho$ term, to compute the
new base state density,
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left [ \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j+\myhalf} -  
         \left( {{\rho}_0}^{\outp,\nph} {w_0}^{\inp}\right)_{j-\myhalf} \right ] \nonumber  \enskip,
\end{eqnarray}
where $j$ refers to the one-dimensional index in the radial direction.
The interface states, ${{\rho}_0}^{\outp,\nph}$, are found via the
procedure described in paper II, Appendix A, and are saved for use
later in the overall algorithm.

@@

\item[spherical:]

@@

\item {\bf Correct Base}$(\rho_0^{\inp} , \etarho^{\inp}) \rightarrow (\rho_0^{\outp})$
is the process by which we adjust the base state density to account for
large-scale mixing, through $\etarho$

\item[plane-parallel:] We use
\begin{eqnarray}
\rho_{0,j}^{\outp} &=& \rho_{0,j}^{\inp} - \frac{\dt}{\dr} 
\left( \eta_{\rho,j+\myhalf}^{\inp} - \eta_{\rho,j-\myhalf}^{\inp}  \right)  \enskip . 
\end{eqnarray}

\item[spherical:] ~

\MarginPar{need to add spherical}

@@

@@

\item Construct $w_0^{\nph,\star}$

\item[plane-parallel:] We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g \enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh},$ \MarginPar{note: this is true only for plane-parallel}
\MarginPar{Need dpdt\_factor stuff.}
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}} \psi^{\nmh} \enskip . \nonumber
\end{equation}

\item[spherical:] ~

\MarginPar{need to add spherical}

@@

The local velocity field is described by

@@

\item Evolve $(\rho X_k)^{(1)} \rightarrow (\rho X_k)^{(2),\star}$ and
$(\rho h)^{(1)} \rightarrow (\rho h)^{(2),\star}$ without explicitly including the 
reaction terms,
\begin{eqnarray}
(\rho X_k)^{(2),\star} &=& (\rho X_k)^{(1)} 
 - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho X_k)^{(1),\nph,\star} \right) \right] \enskip , \\ \nonumber  \\
(\rho h)^{(2'),\star} &=& (\rho h)^{(1)} - \dt \; \left[ \nablab \cdotb \left( (\uadvone+w_0^{\nph,\star} \er)  
  (\rho h)^{(1),\nph,\star} \right) \right] \nonumber \\
&& + \dt \; \left(\uadvone \cdotb \er\right) \left(\frac{\partial p_0}{\partial r} \right)^{n} 
+ \dt \; \psi^{\nmh} \enskip , \\
\rho^{(2'),\star} &=& \sum_k (\rho X_k)^{(2),\star} \enskip , \\ 
X_k^{(2),\star} &=& (\rho X_k)^{(2),\star} / \rho^{(2),\star}
\end{eqnarray}
\MarginPar{why $\rho^{(2'),\star}$ and not $\rho^{(2),\star}$?}
\item {\bf Correct Base}$(\rho_0^{(2),\star}, \etarho^{\nmh}) \rightarrow (\rho_0^{n+1,\star})$.

@@

\begin{description}
\item[plane-parallel:]~

@@

\item[spherical:]~

\MarginPar{need to add spherical here}
\end{description}

@@

\item {\bf React State}$[ \rho^{(2),\star},(\rho h)^{(2),\star}, X_k^{(2),\star}, 
                             T^{(2),\star}, (\rho^{(2),\star} \Hext)] $\\
$\rightarrow [ \rho^{n+1,\star},(\rho h)^{n+1,\star}, X_k^{n+1,\star}, T^{n+1,\star}, 
              (\rho \omegadot_k)^{(2),\star}, (\rho \Hnuc)^{(2),\star} ].$

@@

\item Construct $w_0^{\nph}$

\item[plane-parallel:] We integrate equation (\ref{eq:divw0}),

@@

\item[spherical:]~

@@

\item[plane-parallel:] ~

@@

\item {\bf React State}$[\rho^{(2)},(\rho h)^{(2)}, X_k^{(2)},T^{(2)}, (\rho^{(2)} \Hext) ]
                   \rightarrow [\rho^{n+1}, (\rho h)^{n+1}, X_k^{n+1}, T^{n+1}, 
                               (\rho \omegadot_k)^{(2)}, (\rho \Hnuc)^{(2)} ].$

@@

  \item {\bf React State}$[ \rho^{\initp},(\rho h)^{\initp}, X_k^{\initp}, T^{\initp}, (\rho^{\initp} \Hext) ]$\\
      $\rightarrow [\rho^{\outp}, (\rho h)^{\outp}, X_k^{\outp}, T^{\outp}, (\rho \omegadot_k)^{0,\nu} ].$
